Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2014-07-20 cordillera-cycle.tex
Change author list and add contributions.

% Authors
\Author[1,2]{J.}{Seguinot}
\Author[2]{I.}{Rogozhina}
\Author[3]{M.}{Margold}
\Author[1]{J.}{Kleman}
\Author[1]{A.~P.}{Stroeven}
\runningauthor{J.~Seguinot et~al.}
\correspondence{J.~Seguinot (julien.seguinot@natgeo.su.se)}

@@

% Author contributions
\section*{Author contributions}
\dots

>>>>

% Authors
\Author[1,2]{J.}{Seguinot}
\Author[2]{I.}{Rogozhina}
\Author[1]{A.~P.}{Stroeven}
\Author[3]{M.}{Margold}
\Author[1]{J.}{Kleman}
\runningauthor{J.~Seguinot et~al.}
\correspondence{J.~Seguinot (julien.seguinot@natgeo.su.se)}

@@

% Author contributions
\section*{Author contributions}
J.~Seguinot ran the simulations and wrote most of the manuscript; I.~Rogozhina
guided experiment design; A.~P.~Stroeven, M.~Margold and J.~Kleman took part in
the interpretation and comparison of model results against geological evidence.
All co-authors contributed to improve the text.
